%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Kunz Leigh \& Associates} % Organization
    {Okemos, Michigan} % Location
    {June. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Inspectors within the Michigan Department of Agriculture operated on both an Access database and a paper process to conduct inspections, enforce regulations, and issue fines. Kunz Leigh was contracted to digitize and streamline the inspection process within MDARD through a web application for administrators and a mobile application for inspectors.}
      \item {The Public Utilities Commission of Ohio requested a rewrite of a Microsoft Access application using a modern web framework. The resulting software suite consisted of an angular application with a C\# api and a field application written in XAML for the railroad inspectors. The suite manages all information related to railroad crossings, inspections, and enforcements.}
      \item {Developed the Railroad Information System (RRIS) using C\#, Microsoft SQL and Angular. The Railroad Information System is both a web application for administrative work for the Public Utilities Commission of Ohio.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {Software Engineer Coop} % Job title
  {HelloWorld} % Organization
  {Southfield, Michigan} % Location
  {Jan. 2015 - March 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Prototyped an application to augment manual user interface testing for the internal Quality Assurance team as part of the Kettering Thesis.}
    \item {Built backend systems for customer engagement and loyalty platforms for clients such as Kraft, Keurig and Mondelez.}
    \item {Performed data acquisition and reporting using Pentaho and MySql.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Software Engineer Coop} % Job title
  {The MITRE Corp} % Organization
  {Tampa, Florida} % Location
  {June 2012 - Sep. 2014} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Enhanced a baseline of D3JS for an internal suite of corporate management tools.}
      \item {Constructed an application to demonstrate the the usage of a vendor security suite surrounding the DCGS Integrated Backbone to a government agency.}
      \item {Assembled a web interface for geospatial command line tools to create a friendly user experience for analysts.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
